Modelling low Mach number stellar hydrodynamics with MAESTROeX

### 2019-10-03 astronum_2019_MAESTROeX/astronum-maestroex.tex
suite new problems -> suit new problems
Add a sentence about the ignition simple network integration for the reacting bubble test problem to give context for the burn timing.

All codes in the \amrexastro~suite are open source, with all development carried out in public repositories hosted on GitHub\footnote{\url{https://github.com/AMReX-Astro}}. We believe that having both the codes and the development process completely open promotes good scientific practices, as it means that results from our simulations are reproducible and the codes used to produce them can be examined and improved by the community.  Others can use the codes for their own scientific investigations, and it is possible to adapt all or parts of the codes to suite new problems. Using version control allows us to keep a record of the codes' development process, helping us to track down bugs and means that new and existing developers can learn from previous mistakes. The development branches of the codes are tested nightly using a test suite of problems, checking that any new additions to the code have not significantly changed any of the solutions or slowed down the performance.

@@

As mentioned, our work porting \maestroex~to run on GPUs is still ongoing, however in Figure~\ref{fig:gpu_speedup} we show the speedup we have achieved so far for a number of individual functions that have been offloaded to GPU. The plot shows the average execution time of each function, recorded for the three-dimensional \texttt{reacting\_bubble} problem on the OLCF Summit machine. Both tests were run on a single node, consisting of two IBM POWER9 processors (together providing 42 physical CPU cores) and six NVIDIA Volta GPUs. The CPU test used 42 MPI processes, each with 4 OpenMP threads, and the GPU test used 6 MPI processes, each process associated with a single GPU. Note that the plot's $x$-axis scale is logarithmic. As can be seen, large speedups in excess of 30-40$\times$ were achieved for several of the functions when run on the GPU. Once we have finished porting the remaining routines to GPU and further optimised our code, we hope to achieve this sort of speedup for the entire timestep.

>>>>

All codes in the \amrexastro~suite are open source, with all development carried out in public repositories hosted on GitHub\footnote{\url{https://github.com/AMReX-Astro}}. We believe that having both the codes and the development process completely open promotes good scientific practices, as it means that results from our simulations are reproducible and the codes used to produce them can be examined and improved by the community.  Others can use the codes for their own scientific investigations, and it is possible to adapt all or parts of the codes to suit new problems. Using version control allows us to keep a record of the codes' development process, helping us to track down bugs and means that new and existing developers can learn from previous mistakes. The development branches of the codes are tested nightly using a test suite of problems, checking that any new additions to the code have not significantly changed any of the solutions or slowed down the performance.

@@

As mentioned, our work porting \maestroex~to run on GPUs is still ongoing, however in Figure~\ref{fig:gpu_speedup} we show the speedup we have achieved so far for a number of individual functions that have been offloaded to GPU. The plot shows the average execution time of each function, recorded for the three-dimensional \texttt{reacting\_bubble} problem on the OLCF Summit machine.
This problem uses a simple reaction network modelling $^{12}\mathrm{C} + {}^{12}\mathrm{C} \rightarrow {}^{24}\mathrm{Mg}$ integrated on the GPUs using the CUDA Fortran port of VODE \citep{vode} described in \cite{Zingale2018}.
Both tests were run on a single node, consisting of two IBM POWER9 processors (together providing 42 physical CPU cores) and six NVIDIA Volta GPUs. The CPU test used 42 MPI processes, each with 4 OpenMP threads, and the GPU test used 6 MPI processes, each process associated with a single GPU.
Note that the plot's $x$-axis scale is logarithmic. As can be seen, large speedups in excess of 30-40$\times$ were achieved for several of the functions when run on the GPU. Once we have finished porting the remaining routines to GPU and further optimised our code, we hope to achieve this sort of speedup for the entire timestep.
